Establishing Trusted I/O Paths for Client \\ Shielded Execution Systems with Aurora

### 2019-07-03 sections/main.tex
sqlite tpc-h benchmark ; grammar checks

@@

We evaluated the enhanced SQLite performance by inserting a randomly generated record to a big table for 1000 times. To make a fair comparison, we set the synchronize flag to "FULL" to avoid the uncertainty of I/O caching. When SGX-SQLite invokes Tlibaurora file APIs, it opens the USB storage device as a raw block file in direct I/O mode and reads/writes data using 4KB block size. In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds. About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}. %Since the USB DMA transfer is designed as an asynchronous mechanism, the delay is not that explicit. 
%We plan to combine with existing in-enclave filesystem support~\cite{OBLIVIATE2018} for \textsc{Aurora}'s trusted storage path.

@@

For comparison, we measured the performance of other clock providers. The results are shown in \autoref{table:timeservice}. Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks like timing attacks. 
Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row). 
%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.

To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we used \emph{dd} program with options "fsync" and "direct" to write variable sizes of contents to a USB mass storage device on native Linux system as the baseline. To avoid the side-effect of any buffer mechanism, we use Linux raw device to mount and initialize the USB device. % to bypass any file system interference. We then measure the overheads of using Aurora's SMVisor for MAC verification added to each block request in the request and response path. We did not use any encryption in this experiment. 
The throughput results are shown in \autoref{table:dd} where the size of each block is set to 4KB. \textsc{Aurora} achieves approximately 90\% of the baseline throughput when writing 1GB to device. The major overheads are contributed by SMM/Protected mode transitions and cryptographic computations on each block.

>>>>

For comparison, we measured the performance of other clock providers. The results are shown in \autoref{table:timeservice}. Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks. 
Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row). 
%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.

To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we used \emph{dd} program with options \textsf{fsync} and \textsf{direct} to write variable sizes of contents to a USB mass storage device on native Linux system as the baseline. To avoid the side-effect of any buffer mechanism, we use Linux raw device to mount and initialize the USB device. % to bypass any file system interference. We then measure the overheads of using Aurora's SMVisor for MAC verification added to each block request in the request and response path. We did not use any encryption in this experiment. 
The throughput results are shown in \autoref{table:dd} where the size of each block is set to 4KB. \textsc{Aurora} achieves approximately 90\% of the baseline throughput when writing 1GB to device. The major overheads are contributed by SMM/Protected mode transitions and cryptographic computations on each block.

@@

\begin{table}	
	\centering
	\caption{TPC-H benchmark comparison between native SGX-SQLite and \textsc{Aurora}-SQLite.}
	\label{table:tpch}
	\small
	\begin{tabular}{lrrr}
		\toprule
		\textbf{Query} & \textbf{SGX-SQLite(s)} & \textbf{Aurora-SQLite(s)} & \textbf{Slowdown(\%)} \\
		\midrule
		02 & 4.68 & 5.10 & 8.97 \\
		11 & 1.29 & 1.42 & 10.08 \\
		16 & 1.08 & 1.10 & 5.30 \\
		17 & 91.26 & 93.30 & 2.23 \\
		18 & 24.98 & 25.91 & 3.72 \\
		19 & 93.15 & 98.25 & 5.47 \\
		21 & 39.68 & 43.16 & 9.04 \\
		\bottomrule
	\end{tabular}
\end{table}

We evaluated the enhanced SQLite performance by running standardized TPC-H benchmark\footnote{http://www.tpc.org/tpch/} over a large database. % (around 1.3GB).
We modified the benchmark queries in order to make them possible to be executed in SQLite. Unfortunately, not all queries can be executed.
To directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, we set the synchronize flag to \textsf{FULL} to avoid the uncertainty of I/O caching. When SQLite invokes Tlibaurora file APIs, it opens the USB storage device in direct I/O mode and reads/writes data using 4KB block size.
%In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds. About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.

\autoref{table:tpch} shows the successfully executed queries and their results of native SGX-SQLite and \textsc{Aurora}-SGLite respectively. In our experiments, no more than 10.08\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
Note that these are the worst-case overheads (because we have set \textsf{PRAGMA synchronous} to \textsf{FULL}) as almost all databases have their own optimized caching mechanisms for better performance.

@@
